---
title: "Math Games"
---

### A Little Number Game

Source: https://twitter.com/NeilShenvi/status/1682736373118255104

Problem Summary: I choose an integer between 1-100. You try to guess it using as few questions as possible by asking either:

#1 "Is the number > 20?"
or
#2 "Is the number X?" (you can ask this many times using different Xs)

Should you ask #1 and then ask #2 repeatedly?

The solution provided by the asker involved game theory, but I approached the problem purely from the standpoint of the initial
random number being a discrete uniform random variable take the value of an integer from 1 to 100.

Based on my empirical simulations below, the expected value of the number of questions to reach the true number using each method (asking #1 first and then repeatedly asking #2 vs. only asking #2 from the outset) seems to be equal, as well as the median and variance.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=TRUE, message=FALSE, warning=FALSE}
#Neil Shenvi's math game

#Set seed for replicability, and number of simulation iterations
set.seed(7232023)
sim_iters <- 10000000

#Strategy 1 - Ask whether number is <= 20, then guess numbers
guesses <- numeric(sim_iters)
for(i in 1:sim_iters){
  iter_guess <- 0
  cands <- 1:100
  correct <- FALSE
  #Draw number
  number <- sample(cands,1)
  #Ask first question
  if(number <= 20){
    cands <- 1:20
  } else{
    cands <- 21:100
  }
  iter_guess <- iter_guess + 1
  #Now repeatedly make random guesses
  while(!correct){
    #Get guess
    num_guess <- sample(cands,1)
    iter_guess <- iter_guess + 1
    #See if it's correct
    correct <- (num_guess == number)
    #Remove it from consideration
    cands <- cands[cands != num_guess]
  }
  #Record result
  guesses[i] <- num_guess
}
#Summary statistics
cat("Empirical mean number of guesses for ", sim_iters," iterations is ",mean(guesses),"\n")
cat("Empirical variance of number of guesses for ", sim_iters," iterations is ",var(guesses),"\n")
cat("Empirical median number of guesses for ", sim_iters," iterations is ",median(guesses),"\n")

#Strategy 2 - Just guess numbers
guesses <- numeric(sim_iters)
for(i in 1:sim_iters){
  iter_guess <- 0
  cands <- 1:100
  correct <- FALSE
  #Draw number
  number <- sample(cands,1)
  #Now repeatedly make random guesses
  while(!correct){
    #Get guess
    num_guess <- sample(cands,1)
    iter_guess <- iter_guess + 1
    #See if it's correct
    correct <- (num_guess == number)
    #Remove it from consideration
    cands <- cands[cands != num_guess]
  }
  #Record result
  guesses[i] <- num_guess
}
#Summary statistics
cat("Empirical mean number of guesses for ", sim_iters," iterations is ",mean(guesses),"\n")
cat("Empirical variance of number of guesses for ", sim_iters," iterations is ",var(guesses),"\n")
cat("Empirical median number of guesses for ", sim_iters," iterations is ",median(guesses),"\n")



```
