---
title: "Generate MC Groups"
---

### Generate Groups for MC

Some code that generates groups for MC. It uses something akin to an adjacency matrix to weight pairings of people
as less likely to occur in this iteration the more that they've occurred in previous iterations.

The below output will generate three groups based on the algorithm I've devised and the current attendees. Not all possible
groups of 3 are considered as this is a prohibitively large number of possibilities, but 10,000 random representative groupings
are considered. Additionally, if Haley and Alex are both in attendance, then they are forced to be in different groups, as
this is one of the constraints of the problem.

```{r, echo = FALSE}
#Source external files
source("scripts/generate_previous_groups.R")
source("scripts/generate_mc_groups.R")

```

```{r}
#########################
### Run for this week ###
#########################
#Set attendees
attendees <- c("Alex","Haley","Scott","Arianna","Jesse","Holly","Russ","Lauren","Sam","Bronson",
                  "Mike","Carol","Steve","Martin","Jordan","Tracy","Amanda","Tara","Kelsey","Amy","Matt")
#Set seed for today to ensure replicability
set.seed(as.integer(Sys.Date()))

generate_mc_groups(attendees, all_dates)

```
